---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/",
  out.width = "100%"
)
```

# DAGmin

<!-- badges: start -->
<!-- badges: end -->

DAGmin is an R package that implements an algorithm for the enumeration of all minimally-sized covers (exact or not) of a set X that are consistent with relationships established by a directed acyclic graph (DAG).   Covers are formed from combinations of defined subsets of X, and each defined subset is mapped to a node of a DAG. 

An acceptable cover meets three criteria:

(1) The coverage property: The union of all subsets contained in the cover is the set X.
(2) The DAG-consistency property:  If i -> j is an edge in the DAG, then any cover that includes subset i must also include subset j.
(3) The minimality property: If any subset is removed from the cover, it breaks properties (1) or (2) or both.

## Installation in R

This package is in the development stage! Feedback and questions are welcome.

Code is available at https://github.com/robert-rovetti/DAGmin.  You can install the development version of DAGmin in R by running:

``` r
library(pak)
pak("robert-rovetti/DAGmin")
```

## Example

Let's start with a simple set X = {x1, x2, x3, x4, x5}, and then take various subsets of X.  The subsets are named s1 through s8, and together form the family S of subsets.
```{r side_by_side, echo=FALSE, fig.align='center'}
library(cowplot)
ggdraw() + 
  draw_image("man/figures/S.png", width = 0.4) + 
  draw_image("man/figures/G.png", width = 0.4, x = 0.5)
```
The subsets are also related to each other through this DAG, where the arrows indicate _requirement_. 

The goal is to find various combinations of the subsets such that all elements of X are represented at least once (duplications are OK), _and_ such that the requirement criteria are also met, _and_ such that the combinations are "minimal" in size (ie, no unnecessary subsets).

Both the subset matrix and the DAG adjacency matrix can be represented by zero-one matrices:

```{r example}
S <- as.matrix(read.csv('http://dagmin.rovero.org/data/S.csv', header=FALSE, row.names=NULL))
G <- as.matrix(read.csv('http://dagmin.rovero.org/data/G.csv', header=FALSE, row.names=NULL))

S

G
```
Calling DAGmin is a simple matter of supplying the subset matrix (S) and the DAG adjacency matrix (G):
```{r example2}
library(DAGmin)
results <- dagmin(S,G)
```
We can view the generated covers to see which subsets are in each cover:
```{r example 3}
results$covers
```
